%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Copyright (c) 2021, 2022     %
%          Daylam Tayari           %
%                                  %
%  Credit to Pascal-0x90 for the   %
%     original LaTeX template.     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass{article}
\usepackage[cm]{fullpage}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{xifthen}
\hypersetup{breaklinks=true,%
	pagecolor=white,%
	colorlinks=true,%
	linkcolor=cyan,%
	urlcolor=MyDarkBlue}
\definecolor{MyDarkBlue}{rgb}{0,0.0,0.45}


%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting parameters  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newlength{\tabin}
\setlength{\tabin}{1em}
\newlength{\secsep}
\setlength{\secsep}{0.1cm}
\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}
\definecolor{contactgray}{gray}{0.2}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Template Definitions  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-6pt} \hrulefill \\ \vspace*{-15pt}}
\newcommand{\name}[1]{\begin{center}\textsc{\Large#1}\\\end{center}}
\newcommand{\program}[1]{\begin{center}\textsc{#1}\end{center}}
\newcommand{\contact}[1]{\begin{center}\color{contactgray}{\normalsize#1}\end{center}}

\newenvironment{tabbedsection}[1]{
	\begin{list}{}{
			\setlength{\itemsep}{0pt}
			\setlength{\labelsep}{0pt}
			\setlength{\labelwidth}{0pt}
			\setlength{\leftmargin}{0pt}
			\setlength{\rightmargin}{\tabin}
			\setlength{\listparindent}{0pt}
			\setlength{\parsep}{0pt}
			\setlength{\parskip}{0pt}
			\setlength{\partopsep}{0pt}
			\setlength{\topsep}{#1}
		}
		\item[]
	}{\end{list}}

\newenvironment{nospacetabbing}{
	\begin{tabbing}
	}{\end{tabbing}\vspace{-1.2em}}

\newenvironment{resume_header}{}{\vspace{0pt}}

\newenvironment{resume_section}[1]{
	\filbreak
	\vspace{2\secsep}
	\textsc{\color{blue}\large#1}
	\lineunder
	\begin{tabbedsection}{\secsep}
	}{\end{tabbedsection}}

% Variable 1: Date; Variable 2: Subsection name.
\newenvironment{resume_subsection}[2]{
	\textbf{\color{BlueViolet}#2} \hfill {\normalsize (#1)} \hspace{-5em}
	\begin{tabbedsection}{0.5\secsep}
		\begin{subitems}
		}{\end{subitems}\end{tabbedsection}}

% Variable 1: Date; Variable 2: Subsection name.
\newenvironment{resume_project_subsection}[3]{
	\textbf{\color{BlueViolet}#2} \hfill \hspace{-5em} {\normalsize (#1)}
	\\ {\small \textit{ #3}}
	\begin{tabbedsection}{0.5\secsep}
		\begin{subitems}
		}{\end{subitems}\end{tabbedsection}}

\newenvironment{subitems}{
	\renewcommand{\labelitemi}{-}
	\begin{itemize}
		\setlength{\labelsep}{1em}
	}{\end{itemize}}

% If you only had a single role, put your role as the second value otherwise use the resume_position environment inside of this environment.
% Variable 1: Company name; Variable 2: Role/title; Variable 3: Years worked.
\newenvironment{resume_employer}[3]{
	\begin{tabular*}
		{1.0\textwidth}{@{\extracolsep{\fill}} l l r}
		\textbf{#1} & \textbf{#2} & \textbf{#3}
	\end{tabular*}
}

% To establish a section with in the projects that the following bullet points will point to a pariticular skill.
% Variable 1: Skill title.
\newenvironment{resume_skill_group}[1]{
	\hspace{-18pt}\textbf{#1}
	\begin{itemize}
	}{\end{itemize}}

% Variable 1: Role/title; Variable 2: Years holding that role.
\newenvironment{resume_position}[2]{
	\vspace{\secsep}
	\textbf{#1} \hfill {\normalsize (#2)} \hspace{-2.64em}
	\begin{subitems}
	}{\end{subitems}}

%%%%%%%%%%%%%%%%%%%%
%     Document     %
%%%%%%%%%%%%%%%%%%%%

\begin{document}
	
	\begin{resume_header}
		\name{Eric Lagnese}
		\contact {
			\faEnvelope[solid] \, \href{mailto:etlagnese@gmail.com}{etlagnese@gmail.com}
			\faPhone \, \href{tel:724-759-0944}724-759-0944
		}
		\contact {
			 \faLinkedin \, \href{https://www.linkedin.com/in/eric-lagnese/}{eric-lagnese}
			 \faHome \, 707 N Hickory Ave. Apt. 3, 21014
		}
	\end{resume_header}
	
	%\begin{resume_section}{Objective}
	%Highly driven student with experience working with a large variety of technologies and enterprise solutions seeking a security internship.
	%\end{resume_section}

	\begin{resume_section}{Work Experience}
		\begin{resume_employer}{Software Engineer}{June (2019) - Present}{AASKI Technology aq. by MAG Aerospace}
			Operated in a small team that produced software applications for soldier use in the field. Main area of focus was on frontend
			development. Additionally consolidated and fulfilled requirements provided by the customer. Debugged networks, linux services, and
			android applications.
		\end{resume_employer}
		\begin{resume_employer}{Intern}{Summer (2018)}{AASKI Technology}
Completed Full-Stack development of User Interface using Golang, HTML, and Vue.js. Implemented solutions for a dynamic User
Interface and dynamic data-binding. Assisted implementation of server and databases on embedded devices.
		\end{resume_employer}
		\begin{resume_employer}{Research Volunteer}{October (2016) - May (2017)}{WVU School of Medicine}
		Contributed in Neural Engineering Laboratory to DARPA HAPTIX subcontract (PI: Yakovenko). Responsible for signal processing of
		kinematics, surface and intramuscular electromyography from healthy and amputee human subjects.
		\end{resume_employer}
	\end{resume_section}
	
	\vspace{2\secsep}	
	
	\begin{resume_section}{Education}
		\begin{resume_subsection}{August 2015 - May 2019}{West Virginia University}
			B.S. in Mechanical Engineering \hspace{8.75cm}	\makebox[2cm]{GPA: 3.73}\par
			Minor in Computer Science  \hspace{9cm} \makebox[5cm]{Completed Hours: 152}\\*
		\end{resume_subsection}
	\end{resume_section}
	
	\vspace{-3\secsep}
	
	\begin{resume_section}{Projects}
		\begin{resume_project_subsection}{August 2022 - Present}{Mounted Mission Command}{An \textbf{Android Open Source Project} (AOSP) and \textbf{Yocto Linux} project for Mounted Computing on military vehicles.}
			\begin{resume_skill_group}{Project Management}
				\item 
				\item 
				Worked as a developer on a team of \textbf{16 engineers} to develop a product release for soldiers. 
				\item 
				Organized discussions from the customer to form an actionable report to the developers.
				\iffalse
				\item 
				Formed most of the team’s documentation for testing, building, and development environments to support our team of developers that has doubled in size. 
				
				\fi
			\end{resume_skill_group}
			
			\begin{resume_skill_group}{Development}
				\item 
				\item  
				Developed user applications in \textbf{C and Java} with their \textbf{BitBake} recipes for networking and user interface. 
				\item 
				Completed critical UX feature for customer saving money and potential late delivery.
				\item 
				Lead development to customize for new deployment target; AOSP build management to support multiple custom lunch targets. Debugged boot, customized networking management and input management.
				\item
				Debugging the linux kernel via kgdboe and QEMU.
				\item
				Managed AOSP kernel updates
				\item
				Created login application that acted as a Device Policy Manager; Performed application hardening from penetration test results.
			\end{resume_skill_group}
		\end{resume_project_subsection}
		\vspace{2\secsep}
		\begin{resume_project_subsection}{August 2019 - Present}{Precision Fires-Dismounted}{Precision Fires-Dismounted (PF-D) is an Android App that runs as a plugin to a geospatial awareness \textbf{Android App}.}			
			\begin{resume_skill_group}{Project Management}
				\item 
				\item 
					Consolidated project requirements to support project management. 
				\item 
					Interfaced with the developers assigning and distributing the workload after receiving test reports.
				\item 
					Assisted with the fielding of this product as well as relaying and finding technical solutions to the customer. 
				\end{resume_skill_group}
				
				\begin{resume_skill_group}{Development}
						\item 
				
					\item
					Developed both \textbf{Java and C} for Android working with networking and user interface (UI).
					\item
					Implemented user experience (UX) improvements, backend support for network
					management, performance improvements for UI responsiveness, and worked to remove technical debt. 
					\iffalse
					\item 
					Implemented basic geographical calculations. 
					\item 
					Initiated the development of a code generation tool to implement a standard message specification. 
					\fi
				\end{resume_skill_group}
		\end{resume_project_subsection}
		\vspace{2\secsep}
		
		\iffalse
		\begin{resume_project_subsection}{June 2019 - September 2019}{Radio Timing Tool}{This application is currently in use to establish the modem timing configurations used to create field networks for tactical digital communications.}
				\item 
					Worked to create a command line interface and assisted in debugging the capturing of timing parameters for \textbf{Python} application.
		\end{resume_project_subsection}
		\vspace{2\secsep}
		\fi
		
		\iffalse
		\begin{resume_subsection}{August 2017 - May 2019}{University Robotics Competition Team}
			\begin{itemize}
				\item 
					As a member of multiple sub teams, using C++ programmed kinematics for Rover’s waypoint navigation, calculated distance of
					objects to Rover given Computer Vision data.
				\item 
					Lead the communications and user interface team.
			\end{itemize}
		\end{resume_subsection}
		\vspace{2\secsep}
		\begin{resume_subsection}{Fall 2018}{Mobile Robotics Project}
			Programmed in C++ to implemented GPS navigation, path planning, and tennis ball (object) detection for autonomous traversal task.
			Using the random error from GPS measurements, created a random searching method. Interfacing programs and data with Robotic
			Operating System. Created simple reactive obstacle avoidance and a waypoint navigation inspired by bug algorithm.
		\end{resume_subsection}
		\fi
	\end{resume_section}
	
	\begin{resume_section}{Skills}
	\begin{nospacetabbing}
		\textbf{Languages:} \hspace{5em} \=Java, C, Python, SQL.\\*
		\textbf{Technologies:} \> PostgreSQL, lxc, QEMU, Docker, Gitlab, Linux, Yocto, IP Networking.\\*
		\textbf{Tools:} \> JetBrains IDE's, neovim, gdb
	\end{nospacetabbing}
	\end{resume_section}
	
\end{document}
